### 2016-09-07 sec6_experiment.tex
Revision inlcluded

\textbf{Environment Setup}: We use Yarn\footnote{\url{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}} to manage our cluster. We pick one machine as Yarn's master node, and for each of the remaining machines, we reserve one core and $2$GB memory for Yarn processes. We deploy our GCMP detector on Apache Spark 1.5.2~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory. In Spark, one of the $55$ executors is taken as the Application Master for coordination, therefore our setting results in $54$ executors. \revised{We set the number of partitions to be $486$ to fully utilize the parallelism provided by the multi-threading of every core.}
All our implementations as well as cluster setups are open-sourced in Github\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}}.

@@

\textbf{Varying $G$}: Figures~\ref{exp:performance_vary} (d),(j),(p) present the performances with increasing $G$.  TRPM is rather sensitive to $G$. When $G$ is relaxed to larger values, more valid patterns would be generated. TPRM has to set a higher replication factor and its running time degrades drastically when $G$ increases from $20$ to $30$. In contrast, with much more effective pruning strategy, our SPARE scales well with $G$. Particularly, SPARE is 14 times faster than TRPM when $G=20$ in GeoLife dataset.

@@

\begin{table}[h]
\small
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Time} & \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
\multirow{2}{*}{Shopping}              & TRPM            & 597                               & 90,859                 & 10,019               \\ %\cline{2-5} 
                                       & SPARE           & 237                               & 33,638                 & 8,613                \\ \hline
\multirow{2}{*}{Geolife}               & TRPM            & 747                               & 106,428                & 18,454               \\ %\cline{2-5} 
                                       & SPARE           & 341                               & 35,343                 & 14,369               \\ \hline
\multirow{2}{*}{Taxi}                  & TRPM            & 3,648                             & 503,460                & 51,691               \\ %\cline{2-5} 
                                       & SPARE           & 580                               & 68,580                & 35,912               \\ \hline
\end{tabular}
\caption{Resources taken for TRPM and SPARE. Time is in seconds representing observed performance. Vcore-seconds is the aggregate of time spent in each core. Memory is in MB representing the actual size of RDDs.}
\label{tbl:resource}
\end{table}
}
%\begin{figure}[h]
%\centering
%	\begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
%        \caption{Shopping vary $O_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
%        \caption{Geolife vary $O_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
%        \caption{Taxi vary $O_r$}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
%        \caption{Shopping vary $T_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
%        \caption{Geolife vary $T_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
%        \caption{Taxi vary $T_r$}
%    \end{subfigure}
% \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
% \label{exp:performance_vary_OT}
%\end{figure}

\subsection{Analysis of SPARE framework}
In this part, we extensively evaluate SPARE from three aspects:
(1) the advantages brought by the sequence simplification, (2) the effectiveness of load balance, and (3) the scalability with increasing computing resources.
%Then, we study the scalability of SPARE with increasing computing resources.

@@

\begin{figure}[h]
\centering
	  \includegraphics[width=0.35\textwidth]{/exp/spare/detail1.eps}
    \caption{Breakdown of cost of TRPM, SPARE and SPARE-RD.}
    \label{exp:wl}
\end{figure}

\begin{table}[h]
\centering \small
%\begin{tabular}{|c|c|c|c|c|}
%\hline
%\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
%                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
%Shopping                 & 295              & 41         & 237             & 21       \\ \hline
%GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
%Taxi                     & 681              & 147        & 580             & 96       \\ \hline
%\end{tabular}
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Min} & \textbf{Max} & \textbf{Std. Dev.} 
\\ \hline%\specialrule{1pt}{-0.5pt}{-0.5pt} 
\multirow{3}{*}{Shopping}             % & TRPM            &     426                          & 597                 & 35 \\ %\cline{2-5} 
                                       & SPARE-RD          & 122                               &  295             & 41
\\% \cline{2-5}                                        
									   & SPARE           &  134                              &   237               & 21
\\ \hline                                
\multirow{3}{*}{GeoLife}             % & TRPM            &    493                            & 747                & 78               \\ %\cline{2-5} 
                                       & SPARE-RD          &  38                               &   484               & 148
\\ %\cline{2-5}                                        
									   & SPARE           &   107                             &     341             & 96
\\ \hline
\multirow{3}{*}{Taxi}             % & TRPM            &   3,460                            &    3,648              & 51 \\ %\cline{2-5} 
                                       & SPARE-RD          & 122                               & 681                 & 109
\\ %\cline{2-5}                                        
									   & SPARE           &   134                             &  580                & 56               
\\ \hline
\end{tabular}
  \caption{Statistics of execution time (in seconds) among all executors.}
  \label{tbl:strags}
\end{table}

\subsubsection{Load balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages 
for SPARE and SPARE-RD. %\revised{with TRPM as comparison}. 
We observe that the map and shuffle time of SPARE and SPARE-RD are identical . The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). 
\revised{Meanwhile, both SPARE and SPARE-RD outperform TRPM in each phase. This indicates the 
efficiency of the star partition and apriori enumeration.} 
%\revised{We also report the cost summaries (i.e., longest, shortest and standard deviation) of all jobs for the three methods in Table~\ref{tbl:strags}. As the table shows, SPARE produces more balanced jobs
%than SPARE-RD which verify the effectiveness of the best-fit strategy. In addition, TRPM 
%maintains a low deviation because it uses equal size (i.e., $\eta$) partitioning. 
%However, TRPM still takes much longer time than SPARE algorithms.}
We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
We also report the cost of \revised{the longest job (Max), the shortest job (Min) and the standard deviation (Std. Dev.)}
%\emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) 
for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.

@@

\begin{figure*}[t]
\centering
\begin{subfigure}[b]{0.31\textwidth}
    \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
        \caption{Shopping vary $N$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
        \caption{GeoLife vary $N$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
        \caption{Taxi vary $N$}
    \end{subfigure}
 \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}
 \label{exp:scalability}
\end{figure*}

>>>>

\textbf{Environment Setup}: We use Yarn\footnote{\url{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}} to manage our cluster. We pick one machine as Yarn's master node, and for each of the remaining machines, we reserve one core and $2$GB memory for Yarn processes. We deploy our GCMP detector on Apache Spark 1.5.2~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory. In Spark, one of the $55$ executors is taken as the Application Master for coordination, therefore our setting results in $54$ executors. \revised{We set the number of partitions to be $486$ to fully utilize the multi-threading feature of every core.}
All our implementations as well as cluster setups are open-sourced in Github\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}}.

@@

\textbf{Varying $G$}: Figures~\ref{exp:performance_vary} (d),(j),(p) present the performances with increasing $G$.  TRPM is rather sensitive to $G$. When $G$ is relaxed to larger values, more valid patterns would be generated. TPRM has to set a higher replication factor and its running time degrades drastically when $G$ increases from $20$ to $30$. In contrast, with much more effective pruning strategy, SPARE scales well with $G$. Particularly, SPARE is 14 times faster than TRPM when $G=20$ in GeoLife dataset.

@@

\begin{table}[h]
\small
\centering
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} % & \textbf{Time} 
& \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
\multirow{2}{*}{Shopping}              & TRPM           % & 597
                               & 90,859                 & 10,019               \\ %\cline{2-5} 
                                       & SPARE           %& 237
                                                                      & 33,638                 & 8,613                \\ \hline
\multirow{2}{*}{Geolife}               & TRPM            %& 747 
                              & 106,428                & 18,454               \\ %\cline{2-5} 
                                       & SPARE           %& 341 
                                                                     & 35,343                 & 14,369               \\ \hline
\multirow{2}{*}{Taxi}                  & TRPM            %& 3,648  
                           & 503,460                & 51,691               \\ %\cline{2-5} 
                                       & SPARE           %& 580  
                                                                    & 68,580                & 35,912               \\ \hline
\end{tabular}
\caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size of RDDs.}
\label{tbl:resource}
\end{table}
}
%\begin{figure}[h]
%\centering
%	\begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
%        \caption{Shopping vary $O_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
%        \caption{Geolife vary $O_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
%        \caption{Taxi vary $O_r$}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
%        \caption{Shopping vary $T_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
%        \caption{Geolife vary $T_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
%        \caption{Taxi vary $T_r$}
%    \end{subfigure}
% \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
% \label{exp:performance_vary_OT}
%\end{figure}

\vspace{-3mm}
\subsection{Analysis of SPARE framework}
In this part, we extensively evaluate SPARE from three aspects:
(1) the advantages brought by the sequence simplification, (2) the effectiveness of load balance, and (3) the scalability with increasing computing resources.
%Then, we study the scalability of SPARE with increasing computing resources.

@@

\vspace{-3mm}
\begin{figure}[h]
\centering
	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail1.eps}
    \caption{Cost breakdown of TRPM, SPARE and SPARE-RD.}
    \label{exp:wl}
\end{figure}

\vspace{-4mm}
\begin{table}[h]
\centering \small
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Max        & Std. Dev.     & Max       & Std. Dev.      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
%\begin{tabular}{|l|c|c|c|c|}
%\hline
%\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Min} & \textbf{Max} & \textbf{Std. Dev.} 
%\\ \hline%\specialrule{1pt}{-0.5pt}{-0.5pt} 
%\multirow{3}{*}{Shopping}             % & TRPM            &     426                          & 597                 & 35 \\ %\cline{2-5} 
%                                       & SPARE-RD          & 122                               &  295             & 41
%\\% \cline{2-5}                                        
%									   & SPARE           &  134                              &   237               & 21
%\\ \hline                                
%\multirow{3}{*}{GeoLife}             % & TRPM            &    493                            & 747                & 78               \\ %\cline{2-5} 
%                                       & SPARE-RD          &  38                               &   484               & 148
%\\ %\cline{2-5}                                        
%									   & SPARE           &   107                             &     341             & 96
%\\ \hline
%\multirow{3}{*}{Taxi}             % & TRPM            &   3,460                            &    3,648              & 51 \\ %\cline{2-5} 
%                                       & SPARE-RD          & 122                               & 681                 & 109
%\\ %\cline{2-5}                                        
%									   & SPARE           &   134                             &  580                & 56               
%\\ \hline
%\end{tabular}
  \caption{Statistics of execution time (in seconds) among all jobs.}
  \label{tbl:strags}
\end{table}

\vspace{-2mm}
\subsubsection{Load balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages 
for SPARE and SPARE-RD. %\revised{with TRPM as comparison}. 
We observe that the map and shuffle time of SPARE and SPARE-RD are identical . The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). 
\revised{Meanwhile, both SPARE and SPARE-RD outperform TRPM in each phase. This indicates the 
efficiency of the star partition and apriori enumeration.} 
%\revised{We also report the cost summaries (i.e., longest, shortest and standard deviation) of all jobs for the three methods in Table~\ref{tbl:strags}. As the table shows, SPARE produces more balanced jobs
%than SPARE-RD which verify the effectiveness of the best-fit strategy. In addition, TRPM 
%maintains a low deviation because it uses equal size (i.e., $\eta$) partitioning. 
%However, TRPM still takes much longer time than SPARE algorithms.}
We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
We also report the cost of \revised{the longest job (Max) and the standard deviation (Std. Dev.)}
%\emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) 
for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.

@@

\begin{figure*}[t]
\centering
\begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
        \caption{Shopping vary $N$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
        \caption{GeoLife vary $N$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
        \caption{Taxi vary $N$}
    \end{subfigure}
 \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}
 \label{exp:scalability}
\end{figure*}
